\documentclass[fleqn]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{mathexam}

\ExamClass{CSCE 240}
\ExamName{Homework 1}
\ExamHead{Due: 12 Sept 2018}

\let
\ds
\displaystyle

\begin{document}
\ExamInstrBox {
  You shall submit a zipped, \textbf{and only zipped}, archive of your homework
  directory, hw1. The directory shall contain, at a minimum, the file
  \texttt{draw\_card.cc}.

  I will use my own makefile to make your \texttt{draw\_card.cc} file. Do not
  include use a header for this assignment. My grader will not look for one.
}
%
I have a small gambling interest. I would like an application created which,
when called, reads a single integer $n$, from standard input and emits $n$
randomly drawn cards from $n$ standard 52-card decks. 
%
\vspace{1.0em} \\
The application should perform as follows:
\begin{itemize}
	\item The program is called and runs with no prompt for input.

  \item The program reads an integer from standard input (stdio).

  \item The program should then emit, on a single line delimited by a space the
      cards drawn. You may represent the cards as:\\
      Ace of Spaces: AS \\
      6 of Hearts: 6H \\
      King of Diamonds : KD \\
      2 of Clubs: 2C
\end{itemize}
\vspace{1.0em}
%
I have provided you source for a draw\_card app, a make file, and a test app.
You shall provide me with a compilable file named \texttt{draw\_card.cc}.\\
\\
%
Late assignments will lose 25\% per day late, with no assignment begin accepted
after 4 days (100\% reduction in points).\\
\\
%
Check your syllabus for the breakdown of grading.
\end{document}

